Rates and delay times of type Ia supernovae in the Dark Energy Survey

### 2021-05-21 authlist_end_FR.tex
updating bib

% Author list file generated with: mkauthlist 0+unknown
% mkauthlist DES-2021-0642_author_list_end_CWR.csv authlist_end_CWR.tex -j mnras -a order.txt -f

@@

C.~Frohmaier,$^{1,3}$

@@

D.~Carollo,$^{8}$
T.~M.~Davis,$^{9}$
L.~Galbany,$^{10}$
S.~R.~Hinton,$^{9}$

@@

R.~Kessler,$^{11,12}$
G.~F.~Lewis,$^{13}$
C.~Lidman,$^{14,5}$
A.~M\"oller,$^{15}$

@@

@@

Z.~Zontos,$^{1}$
J.~Asorey,$^{16}$
T.~M.~C.~Abbott,$^{17}$
M.~Aguena,$^{18,19}$

@@

E.~Buckley-Geer,$^{11,20}$

@@

J.~Frieman,$^{20,12}$

@@

A.~Palmese,$^{20,12}$

@@

E.~Sanchez,$^{16}$

@@

I.~Sevilla-Noarbe,$^{16}$

@@

and A.~R.~Walker$^{17}$

@@

$^{8}$ INAF, Osservatorio Astronomico di Trieste, I-34143 Trieste, Italy\\
$^{9}$ School of Mathematics and Physics, University of Queensland,  Brisbane, QLD 4072, Australia\\
$^{10}$ PITT PACC, Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA 15260, USA\\
$^{11}$ Department of Astronomy and Astrophysics, University of Chicago, Chicago, IL 60637, USA\\
$^{12}$ Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA\\
$^{13}$ Sydney Institute for Astronomy, School of Physics, A28, The University of Sydney, NSW 2006, Australia\\
$^{14}$ Centre for Gravitational Astrophysics, College of Science, The Australian National University, ACT 2601, Australia\\
$^{15}$ Universit\'e Clermont Auvergne, CNRS/IN2P3, LPC, F-63000 Clermont-Ferrand, France\\
$^{16}$ Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain\\
$^{17}$ Cerro Tololo Inter-American Observatory, NSF's National Optical-Infrared Astronomy Research Laboratory, Casilla 603, La Serena, Chile\\
$^{18}$ Departamento de F\'isica Matem\'atica, Instituto de F\'isica, Universidade de S\~ao Paulo, CP 66318, S\~ao Paulo, SP, 05314-970, Brazil\\

>>>>

% Author list file generated with: mkauthlist 0+unknown 
% mkauthlist DES-2021-0642_author_list_end_FR.csv authlist_end_FR.tex -j mnras -a order.txt -f

@@

C.~Frohmaier,$^{3,1}$

@@

T.~M.~Davis,$^{8}$
L.~Galbany,$^{9}$
S.~R.~Hinton,$^{8}$

@@

R.~Kessler,$^{10,11}$
C.~Lidman,$^{12,5}$
A.~M\"oller,$^{13}$

@@

Z.~Zontou,$^{1}$
J.~Asorey,$^{14}$
D.~Carollo,$^{15}$
K.~Glazebrook,$^{16}$
G.~F.~Lewis,$^{17}$

@@

T.~M.~C.~Abbott,$^{18}$
M.~Aguena,$^{19}$

@@

E.~Buckley-Geer,$^{10,20}$

@@

J.~Frieman,$^{20,11}$

@@

A.~Palmese,$^{20,11}$

@@

E.~Sanchez,$^{14}$

@@

I.~Sevilla-Noarbe,$^{14}$
M.~Soares-Santos,$^{36}$

@@

and A.~R.~Walker$^{18}$

@@

$^{8}$ School of Mathematics and Physics, University of Queensland,  Brisbane, QLD 4072, Australia\\
$^{9}$ PITT PACC, Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA 15260, USA\\
$^{10}$ Department of Astronomy and Astrophysics, University of Chicago, Chicago, IL 60637, USA\\
$^{11}$ Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA\\
$^{12}$ Centre for Gravitational Astrophysics, College of Science, The Australian National University, ACT 2601, Australia\\
$^{13}$ Universit\{'e} Clermont Auvergne, CNRS/IN2P3, LPC, F-63000 Clermont-Ferrand, France\\
$^{14}$ Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain\\
$^{15}$ INAF, Osservatorio Astronomico di Trieste, I-34143 Trieste, Italy\\
$^{16}$ Centre for Astrophysics \& Supercomputing, Swinburne University of Technology, Victoria 3122, Australia\\
$^{17}$ Sydney Institute for Astronomy, School of Physics, A28, The University of Sydney, NSW 2006, Australia\\
$^{18}$ Cerro Tololo Inter-American Observatory, NSF's National Optical-Infrared Astronomy Research Laboratory, Casilla 603, La Serena, Chile\\
